CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-07 paper_I/ms.tex
[wip] update target table
cdips target table now good

%FIXME: make table

@@

%FIXME: make table
The resulting CDIPS target star list is given in Table~\ref{tbl:cdips_targets}.
The cumulative distribution of target star brightnesses, as well as a
histogram of the ages, is shown in Figure~\ref{fig:cdips_targets}.
Relative to field stars, our target star sample is young, with a
typical age of 100$\,$Myr.

@@

\begin{deluxetable}{lll}
    \tablecaption{CDIPS target stars collected for the present work.  
    \label{tbl:cdips_targets}}
    \tablenum{1}

    \tablecomments{
        Table~\ref{tbl:cdips_targets} is published in its entirety in a 
        machine-readable format.
        A portion is shown here for guidance regarding its form and content.
    }

>>>>

@@

The resulting CDIPS target star list is given in
Table~\ref{tbl:cdips_targets}.  The cumulative distribution of target
star brightnesses, as well as a histogram of the ages, is shown in
Figure~\ref{fig:cdips_targets}.  Relative to field stars, our target
star sample is young, with a typical age of 100$\,$Myr.

@@

\begin{deluxetable*}{lllll}

	\tabletypesize{\footnotesize}

    \tablecaption{
    	CDIPS target star catalog, \texttt{v0.3}.
    	\label{tbl:cdips_targets}
	}
    \tablenum{1}

    \tablehead{
      \colhead{ID} &
      \colhead{497093746702988672} &
      \colhead{2006361919000756992} &
      \colhead{2048442943413035776} & 
      \colhead{5867618572762132864}
    }

    \startdata
    \input{table_cdips_targets.tex}
    \enddata

    \tablecomments{
    This table is published in its entirety in a 
    machine-readable format.
    A portion of the transposed version
    is shown here for guidance regarding its form and content.
    Each row in the machine-readable version (each column in this
    version) represents a target star.
    The unique identifier, ``ID'', is the Gaia-DR2 source identifier.
    The external catalog(s) claiming cluster membership is given 
    as a comma-separated string in
    ``Reference'', and the name they assign is given as a comma-separated
    string in ``Cluster''.
    ``Ext catalog name'' is the name the external catalog assigns.
    Positions, proper motions, and the parallax are from Gaia-DR2.
    The magnitudes in Gaia $G$, $G_{\rm Bp}$, and $G_{\rm Rp}$ bands
    is given.
    The naming matching described in Appendix~\ref{appendix:uniquenames}
    most often succeeds in finding the
    \citet{Kharchenko_et_al_2013} (K13) cluster corresponding to
    the external catalog claiming membership.
    This, or else the external name is used to assign the unique
    cluster name.
    The method for name matching (Appendix~\ref{appendix:uniquenames}) is
    also given as a string, as is a ``Comment'' summarizing
    information from \citet{Kharchenko_et_al_2013} about the
    cluster.
    The age and error as quoted by \citet{Kharchenko_et_al_2013}
    are also given.
}

\end{deluxetable*}

### 2019-08-07 paper_I/table_cdips_targets.tex
cdips target table now good

 497093746702988672 &  2006361919000756992 &  2048442943413035776 &  5867618572762132864 \\
          Platais 3 &             ASCC 121 &           Teutsch 35 &           Loden\_1152 \\
           Dias2014 &             Dias2014 &             Dias2014 &       Kharchenko2013 \\
         799-012054 &           724-092321 &           630-074483 &            650278772 \\
            71.4458 &              337.708 &              294.081 &              209.832 \\
            69.6454 &              54.6607 &              35.8782 &             -59.2883 \\
            -5.1826 &             -3.48356 &             -3.19716 &              -3.6399 \\
          -0.478063 &             -1.28297 &             -2.04354 &             -3.93699 \\
           0.579745 &             0.196117 &             0.324896 &             0.397703 \\
            15.1735 &              15.4843 &              15.1863 &              16.4277 \\
            15.5786 &              16.3805 &              15.7505 &               16.991 \\
            14.6008 &              14.5227 &              14.4853 &              15.6807 \\
          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
       string\_match &         string\_match &         string\_match &         string\_match \\
              False &                False &                False &                False \\
                NaN &                  NaN &                  NaN &                  NaN \\
                8.8 &                  6.4 &                 8.39 &                8.065 \\
                NaN &                  NaN &                  NaN &                0.092 \\

>>>>

 Cluster &                                                 Platais 3 &             ASCC 121 &           Teutsch 35 &           Loden\_1152 \\
 Reference &                                                Dias2014 &             Dias2014 &             Dias2014 &       Kharchenko2013 \\
 Ext catalog name &                                       799-012054 &           724-092321 &           630-074483 &            650278772 \\
 RA &                                                        71.4458 &              337.708 &              294.081 &              209.832 \\
 Dec &                                                       69.6454 &              54.6607 &              35.8782 &             -59.2883 \\
 PMra &                                                      -5.1826 &             -3.48356 &             -3.19716 &              -3.6399 \\
 PMdec &                                                   -0.478063 &             -1.28297 &             -2.04354 &             -3.93699 \\
 Plx &                                                      0.579745 &             0.196117 &             0.324896 &             0.397703 \\
 $G$ &                                                       15.1735 &              15.4843 &              15.1863 &              16.4277 \\
 $G_{\rm Bp}$ &                                              15.5786 &              16.3805 &              15.7505 &               16.991 \\
 $G_{\rm Rp}$ &                                              14.6008 &              14.5227 &              14.4853 &              15.6807 \\
 K13 name match &                                          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
 Unique cluster name &                                     Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
 How match &                                            string\_match &         string\_match &         string\_match &         string\_match \\
 Not in K13? &                                                 False &                False &                False &                False \\
 Comment &                                                       NaN &                  NaN &                  NaN &                  NaN \\
 K13 logt &                                                      8.8 &                  6.4 &                 8.39 &                8.065 \\
 K13 err logt                                                    NaN &                  NaN &                  NaN &                0.092 \\
